Non-kissing and non-crossing complexes \\ for locally gentle algebras

### 2018-07-03 draft/accordionComplexSurfaces.tex
first pictures

% others
\newcommand{\fref}[1]{Figure~\ref{#1}} % reference figures
\newcommand{\ie}{\textit{i.e.}~} % id est
\newcommand{\eg}{\textit{e.g.}~} % exempli gratia
\newcommand{\Eg}{\textit{E.g.}~} % exempli gratia
\newcommand{\apriori}{\textit{a priori}} % a priori
\newcommand{\viceversa}{\textit{vice versa}} % vice versa
\newcommand{\versus}{\textit{vs.}~} % versus
\newcommand{\aka}{\textit{a.k.a.}~} % also known as
\newcommand{\perse}{\textit{per se}} % per se
\newcommand{\ordinal}{\textsuperscript{th}} % th for ordinals
\newcommand{\ordinalst}{\textsuperscript{st}} % st for ordinals
\definecolor{darkblue}{rgb}{0,0,0.7} % darkblue color
\definecolor{green}{RGB}{57,181,74} % green color
\definecolor{violet}{RGB}{147,39,143} % violet color
\newcommand{\darkblue}{\color{darkblue}} % darkblue command
\newcommand{\defn}[1]{\textsl{\darkblue #1}} % emphasis of a definition
\newcommand{\para}[1]{\medskip\noindent\textbf{#1.}} % paragraph
\renewcommand{\topfraction}{1} % possibility to have one page of pictures
\renewcommand{\bottomfraction}{1} % possibility to have one page of pictures
%\renewcommand\labelitemi{$\diamond$} % redefine itemize default symbol
\newcommand{\ex}{_{\textrm{exm}}} % examples
\newcommand{\pa}{_{\textrm{pa}}} % path

@@

\author{Sibylle Schroll}
\address[Sibylle Schroll]{}
\email{schroll@leicester.ac.uk}
\urladdr{\url{}}

@@

\vincent{Examples}
\vincent{Should we introduce Koszul duality here and say what it does on quivers?}

@@

\begin{definition}
\label{defi:koszulDual}
The \defn{Koszul dual} of a locally gentle bound quiver~$\bar Q = (Q,I)$ is the bound quiver~$\bar Q\koszul = (Q\koszul, I\koszul)$ defined as follows:
\begin{itemize}
 \item the quiver~$Q\koszul$ is equal to~$Q$;
 \item the ideal~$I\koszul$ is generated by the paths of length two in~$Q$ that do not appear in~$I$.
\end{itemize}
\end{definition}
\pierreguy{Justify this definition.}
Note that~$\bar Q\koszul$ is gentle, and that~$(\bar Q\koszul)\koszul = \bar Q$.

@@

\begin{definition}
\label{def:surfaceQuiver}
The surface~$\surface(\bar Q)$ of a locally gentle bound quiver~$\bar Q = (Q,I)$ is the orientable surface obtained from the blossoming quiver~$\bar Q\blossom$ as follows:
\begin{itemize}
\item for each arrow~$\alpha \in Q_1\blossom$, consider a lozange~$L(\alpha)$ with four (oriented) sides~$\Enrs{\alpha} = [s(\alpha), v]$, $\Enrt{\alpha} = [v, t(\alpha)]$ (colored green) and~$\Ers{\alpha} = [s(\alpha), v\dual]$ and~$\Ert{\alpha} = [v\dual, t(\alpha)]$ (colored red) as follows:
\vincent{Figure}
\item for any~$\alpha, \beta \in Q_1\blossom$ with~$t(\alpha) = s(\alpha)$, proceed to the following identifications:
    \begin{itemize}
    \item if~$\alpha\beta \in I$, then glue~$\Ert{\alpha}$ with~$\Ers{\beta}$,
    \item if~$\alpha\beta \notin I$, then glue~$\Enrt{\alpha}$ with~$\Enrs{\beta}$.
    \end{itemize}
\end{itemize}
The construction also automatically defines two dual cellular dissections~$\dissection_{\bar Q}$ and~${\dissection_{\bar Q}}\dual$ of the surface~$\surface_{\bar Q}$.
\end{definition}

@@

>>>>

% others
\newcommand{\fref}[1]{Figure~\ref{#1}} % reference figures
\newcommand{\ie}{\textit{i.e.}~} % id est
\newcommand{\eg}{\textit{e.g.}~} % exempli gratia
\newcommand{\Eg}{\textit{E.g.}~} % exempli gratia
\newcommand{\apriori}{\textit{a priori}} % a priori
\newcommand{\viceversa}{\textit{vice versa}} % vice versa
\newcommand{\versus}{\textit{vs.}~} % versus
\newcommand{\aka}{\textit{a.k.a.}~} % also known as
\newcommand{\perse}{\textit{per se}} % per se
\newcommand{\ordinal}{\textsuperscript{th}} % th for ordinals
\newcommand{\ordinalst}{\textsuperscript{st}} % st for ordinals
\definecolor{darkblue}{rgb}{0,0,0.7} % darkblue color
\definecolor{green}{RGB}{57,181,74} % green color
\definecolor{violet}{RGB}{147,39,143} % violet color
\newcommand{\red}{\color{red}} % red command
\newcommand{\green}{\color{green}} % green command
\newcommand{\darkblue}{\color{darkblue}} % darkblue command
\newcommand{\defn}[1]{\textsl{\darkblue #1}} % emphasis of a definition
\newcommand{\para}[1]{\medskip\noindent\textbf{#1.}} % paragraph
\renewcommand{\topfraction}{1} % possibility to have one page of pictures
\renewcommand{\bottomfraction}{1} % possibility to have one page of pictures
%\renewcommand\labelitemi{$\diamond$} % redefine itemize default symbol
\newcommand{\ex}{_{\textrm{exm}}} % examples
\newcommand{\pa}{_{\textrm{pa}}} % path

@@

@@

Examples are represented on \fref{fig:quivers}.

\begin{figure}[t]
	\capstart
	\centerline{\includegraphics[scale=.4]{quivers}}
	\caption{Some locally gentle quivers and their blossoming quivers. Initial vertices are solid and labeled while blossom vertices are hollow, and initial arcs are bold while blossom arcs are thin.}
	\label{fig:quivers}
\end{figure}

\vincent{Should we introduce Koszul duality here and say what it does on quivers?}

@@

\begin{definition}
\label{defi:koszulDual}
The \defn{Koszul dual} of a locally gentle bound quiver~$\bar Q = (Q,I)$ is the bound quiver~$\bar Q\koszul = (Q\koszul, I\koszul)$ defined as follows:
\begin{itemize}
 \item the quiver~$Q\koszul$ is equal to~$Q$;
 \item the ideal~$I\koszul$ is generated by the paths of length two in~$Q$ that do not appear in~$I$.
\end{itemize}
\end{definition}
\pierreguy{Justify this definition.}
Note that~$\bar Q\koszul$ is gentle, and that koszul duality is an involution and commutes with blossoming:~$(\bar Q\koszul)\koszul = \bar Q$ and~$(\bar Q\koszul)\blossom = (\bar Q\blossom)\koszul$.
Examples are represented on \fref{fig:koszulQuivers}.

\begin{figure}[t]
	\capstart
	\centerline{\includegraphics[scale=.4]{koszulQuivers}}
	\caption{The Koszul duals of the (blossoming) quivers of \fref{fig:quivers}.}
	\label{fig:koszulQuivers}
\end{figure}

@@

\begin{definition}
\label{def:surfaceQuiver}
The surface~$\surface(\bar Q)$ of a locally gentle bound quiver~$\bar Q = (Q,I)$ is the surface obtained from the blossoming quiver~$\bar Q\blossom$ as follows:
\begin{enumerate}[(i)]
\item for each arrow~$\alpha \in Q_1\blossom$, consider a lozange~$L(\alpha)$ with four (oriented) sides
\begin{alignat*}{2}
& \Enrs{\alpha} = [v(\alpha), s(\alpha)] \qquad & \Enrt{\alpha} = [v(\alpha), t(\alpha)] \qquad & \text{(colored green)} \\
\text{and} \qquad & \Ers{\alpha} = [v\dual(\alpha), s(\alpha)] \qquad & \Ert{\alpha} = [v\dual(\alpha), t(\alpha)] \qquad & \text{(colored red)}
\end{alignat*}
placed as follows:

\centerline{
\begin{tikzpicture}[scale=2, thick]
	\node (s) at (-1,0) {$s(\alpha)$};
	\node (t) at (1,0) {$t(\alpha)$};
	\node (v) at (0,1) {$\green v(\alpha)$};
	\node (vd) at (0,-1) {$\red v\dual(\alpha)$};
	\draw[color=black, ->] (s) -> (t) node[midway, above] {$\alpha$};
	\pic [draw, angle radius=.7cm] {angle = s--t--vd};
	\pic [draw, angle radius=.7cm] {angle = vd--s--t};
	\draw[color=green, ->] (v) -> (s) node[midway, above left] {$\green \Enrs{\alpha}$};
	\draw[color=green, ->] (v) -> (t) node[midway, above right] {$\green \Enrt{\alpha}$};
	\draw[color=red, ->] (vd) -> (s) node[midway, below left] {$\red \Ers{\alpha}$};
	\draw[color=red, ->] (vd) -> (t) node[midway, below right] {$\red \Ert{\alpha}$};
\end{tikzpicture}
}

\item for any~$\alpha, \beta \in Q_1\blossom$ with~$t(\alpha) = s(\beta)$, proceed to the following identifications:
    \begin{itemize}
    \item if~$\alpha\beta \in I$, then glue~$\Ert{\alpha}$ with~$\Ers{\beta}$,
    \item if~$\alpha\beta \notin I$, then glue~$\Enrt{\alpha}$ with~$\Enrs{\beta}$.
    \end{itemize}
\end{enumerate}
\end{definition}

@@

Definition~\ref{def:surfaceQuiver} constructs an orientable surface~$\surface(\bar Q)$ with boundaries.
This surface is actually endowed with two disjoint sets~$V_{\bar Q}$ and~${V_{\bar Q}}\dual$ of marked points and two dual dissections~$\dissection_{\bar Q}$ and~${\dissection_{\bar Q}}\dual$ defined as follows.

\begin{definition}
\label{def:dissectionQuiver}
The surface~$\surface(\bar Q)$ is endowed with
\begin{itemize}
\item the set~$V_{\bar Q}$ of points~$v(\alpha)$ for~$\alpha \in Q_1\blossom$ after the identifications given by~(ii),
\item the $V_{\bar Q}$-dissection~$\dissection_{\bar Q}$ given by all sides~$\Enrs{\alpha}$ and~$\Enrt{\alpha}$ for~$\alpha \in Q_1\blossom$ after the identifications given by~(ii).
\end{itemize}
The set~${V_{\bar Q}}\dual$ and the ${V_{\bar Q}}\dual$-dissection~${\dissection_{\bar Q}}\dual$ are defined dually.
\end{definition}

\begin{remark}
Observe that
\begin{itemize}
\item $V_{\bar Q}$ has one vertex for each straight walk in~$\bar Q$,
\item $\dissection_{\bar Q}$ has one arc for each vertex~$p \in \bar Q_0$, obtained by concataining the sides~$\Enrt{\alpha} = \Enrs{\beta}$ and~$\Enrt{\alpha'} = \Enrs{\beta'}$ where~$p = t(\alpha) = s(\beta) = t(\alpha') = s(\beta')$, $\alpha\beta \notin I$ and~$\alpha'\beta' \notin I$.
\end{itemize}
A similar remark holds dually for~${V_{\bar Q}}\dual$ and~${\dissection_{\bar Q}}\dual$.
\end{remark}

\begin{example}
Consider the following family of locally gentle quivers:
\vincent{TODO}
\end{example}
